Generate data for NOBA cod ensemble modeling

### 2020-05-29 NOBAcod.Rmd
save new run_truth output

testtruth <- atlantisom::run_truth(scenario = scenario.name,
                       dir = d.name,
                       file_fgs = functional.groups.file,
                       file_bgm = box.file,
                       select_groups = funct.group.names,
                       file_init = initial.conditions.file,
                       file_biolprm = biol.prm.file,
                       file_runprm = run.prm.file,
                       file_fish = fisheries.file,
                       verbose = TRUE,
                       annage = TRUE,
                       save = FALSE
    )

>>>>

testtruth <- atlantisom::run_truth(scenario = scenario.name,
                       dir = d.name,
                       file_fgs = functional.groups.file,
                       file_bgm = box.file,
                       select_groups = funct.group.names,
                       file_init = initial.conditions.file,
                       file_biolprm = biol.prm.file,
                       file_runprm = run.prm.file,
                       file_fish = fisheries.file,
                       verbose = TRUE,
                       annage = TRUE,
                       save = TRUE
    )
